Carbonate chemistry at Ny-Ålesund

### 2022-08-16 awipev-CO2.Rmd
Started to add pCO2 on the REMOS.

Let's look first at the stratification (salinity, temperature and
density).

```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
## Atmospheric CO2 Zeppelin
# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
# value:units : ppm
# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
atm_co2_old <-
  read_delim(file = paste0(path, "atmospheric_co2_zeppelin_old/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
  delim = " ",
  comment = "#",
  #skip = 182,
  col_names = TRUE,
  na = "-999.999",
  show_col_types = FALSE
  ) %>%
  dplyr::mutate(co2_air = value,
  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
  dplyr::select(datetime, co2_air)

>>>>

Let's look at the stratification tab above (salinity, temperature, density and pH).

## pCO2 from pH and AT 0-4m
If one calculates pCO2 from seafet pH and AT (from salinity) between 0-4 m, do we get better estimates of air-sea CO2 fluxes?

```{r}
size_point <- 0.3 # size of data points
alpha <- 1 #transparency
size_labs <- 6 # font size labels

tmp <- d_all %>% 
  dplyr::select(datetime, pHint_tot_sf, sal_insitu_ctd, temp_insitu_ctd) %>% 
  drop_na() %>% 
  dplyr::mutate(at_0_4m = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
                pco2_0_4m = seacarb::carb(flag=8, var1=pHint_tot_sf, var2=tmp$at_0_4m)$pCO2)
ts_pCO2_calc <- tmp %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_0_4m), 
             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title=expression(paste(pCO[2], "calc at 0-4 m and in situ temperature")),
       x="", y=TeX("pCO$_2$ ($\\mu atm$)")) +
  Mytheme(size_labs = size_labs)
ts_pCO2_calc
```

## Atmospheric CO2 Zeppelin
```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
# value:units : ppm
# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
atm_co2_old <-
  read_delim(file = paste0(path, "atmospheric_co2_zeppelin_old/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
  delim = " ",
  comment = "#",
  #skip = 182,
  col_names = TRUE,
  na = "-999.999",
  show_col_types = FALSE
  ) %>%
  dplyr::mutate(co2_air = value,
  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
  dplyr::select(datetime, co2_air)
